---
title: "Rose Data"
author: "Payel Kundu"
date: "5/14/2020"
output: html_document
---
First I load the data
```{r}
library(readxl)
rosedata <- read_excel("RoseData.xlsx")
colnames(rosedata)
```

We want to know what factors predict how strongly a rose smells. First I'll plot smell against size. 
```{r}
ggscatter(rosedata, x = "Smell", y = "Size", 
          add = "reg.line", conf.int = TRUE, 
          cor.coef = TRUE, cor.method = "pearson",
          xlab = "Smell", ylab = "Size")
```
So it looks like the larger the rose is, the less good it smells. The correlation is significant. Next I'll plot smell against color. 
```{r}
ggscatter(rosedata, x = "Smell", y = "Color", 
          add = "reg.line", conf.int = TRUE, 
          cor.coef = TRUE, cor.method = "pearson",
          xlab = "Smell", ylab = "Color")
```
Color does not seem to be a good predictor of smell. They are not significantly correlated. Next I just want to check that my variables are normally distributed. 
```{r}
hist(rosedata$Smell)
hist(rosedata$Size)
```
Size looks pretty good, but smell is skewed towards the lesser smells, we didn't have a lot of roses that smelled strongly. Next I'll check for outliers. 
```{r}
par(mfrow=c(1, 2))
boxplot(rosedata$Smell, main="Color", sub=paste("Outlier rows: ", boxplot.stats(rosedata$Color)$out))
boxplot(rosedata$Size, main="Size", sub=paste("Outlier rows: ", boxplot.stats(rosedata$Size)$out))
```
No outliers in the predictor variables, great! Now I'll build a linear model. 

```{r}
model1 <- lm(Smell ~ Color + Size, data = rosedata)
summary(model1)

```
The model is significant, so we'll use it. I also want to see the interaction between the two factors. 
```{r}
model2 <- lm(Smell ~ Color*Size, data= rosedata)
summary(model2)
```



